DATA 607 Project 2

### 2018-10-02 DATA607/Project_2.Rmd
Additional Work

---
title: "DATA 607 Project 2"
author: "Mike Silva"
date: "October 1, 2018"
output:
  html_document:
    theme: yeti
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

## 2017 United Nations International Migrant Stock

@@

```{r echo=FALSE}
# [http://www.un.org/en/development/desa/population/migration/data/estimates2/docs/MigrationStockDocumentation_2017.pdf](http://www.un.org/en/development/desa/population/migration/data/estimates2/docs/MigrationStockDocumentation_2017.pdf)
# 
# This dataset provides estimates of the international migrant stock by age, sex and origin for the mid-point (1 July) of each year: 1990, 1995, 2000,
# 2005, 2010, 2015 and 2017. 
# 
# Most of the data used to estimate the international migrant stock by country or area were obtained from population censuses. Additionally, population registers and nationally representative surveys provided information on the number and composition of international migrants.
# 
# In estimating the international migrant stock, international migrants have been equated with the foreignborn population whenever this information is available, which is the case in most countries or areas. In most countries lacking data on place of birth, information on the country of citizenship of those enumerated was available, and was used as the basis for the identification of international migrants, thus effectively equating, in these cases, international migrants with foreign citizens.
# 
# Equating international migrants with foreign citizens when estimating the migrant stock has important shortcomings. In countries where citizenship is conferred on the basis of jus sanguinis, people who were born in the country of residence may be included in the number of international migrants even though they may have never lived abroad. Conversely, persons who were born abroad and who naturalized in their 
```

@@

### Parsing Untidy Data

@@

Now I need to clean up the Origins columns.  There are periods that represent spaces.  When there are two periods it needs to be changed into a period and space.  An example of that is Micronesia.(Fed..States.of).

```{r}
un_df <- un_df %>%
  mutate(Origin = str_replace_all(Origin, "[.]", " ")) %>%
  mutate(Origin = str_replace_all(Origin, "  ", ". "))
```

@@

Text

>>>>

---
title: "DATA 607 Project 2"
author: "Mike Silva"
date: "October 1, 2018"
output:
  html_document:
    theme: yeti
    highlight: tango
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

## United Nations International Migrant Stock

@@

### Research Questions

Here are the questions I want to answer with this data:

* What are the top-10 countries receiving/loosing migrants in absolute numbers by year?

* Do communities exist in this network?  Using the number of migrants as the edge between the countries (nodes) in the network graph, do communities emerge from the data?

```{r echo=FALSE}
#### About the Data

# [http://www.un.org/en/development/desa/population/migration/data/estimates2/docs/MigrationStockDocumentation_2017.pdf](http://www.un.org/en/development/desa/population/migration/data/estimates2/docs/MigrationStockDocumentation_2017.pdf)
# 
# This dataset provides estimates of the international migrant stock by age, sex and origin for the mid-point (1 July) of each year: 1990, 1995, 2000,
# 2005, 2010, 2015 and 2017. 
# 
# Most of the data used to estimate the international migrant stock by country or area were obtained from population censuses. Additionally, population registers and nationally representative surveys provided information on the number and composition of international migrants.
# 
# In estimating the international migrant stock, international migrants have been equated with the foreignborn population whenever this information is available, which is the case in most countries or areas. In most countries lacking data on place of birth, information on the country of citizenship of those enumerated was available, and was used as the basis for the identification of international migrants, thus effectively equating, in these cases, international migrants with foreign citizens.
# 
# Equating international migrants with foreign citizens when estimating the migrant stock has important shortcomings. In countries where citizenship is conferred on the basis of jus sanguinis, people who were born in the country of residence may be included in the number of international migrants even though they may have never lived abroad. Conversely, persons who were born abroad and who naturalized in their 
```

@@

### Creating Tidy Data

@@

Now I need to clean up the Origins columns.  There are periods that represent spaces.  When there are two periods it needs to be changed into a period and space.  An example of that is Micronesia.(Fed..States.of).  I will also reorder the columns.

```{r}
un_df <- un_df %>%
  mutate(Origin = str_replace_all(Origin, "[.]", " ")) %>%
  mutate(Origin = str_replace_all(Origin, "  ", ". ")) %>%
  select(Origin, Destination, Migrants, Year)
```

@@

### Analysis

#### Top 10 Receivers of International Migrants

What countries are the top ten in the number of migrants they are receiving by year?
